Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-06-28 theory/figures/fig1.tex
Add section 1 of paper

%Straight Lines [id:da9655093306166109]
\draw    (151.25,213.56) -- (420.92,213.12) ;
%Straight Lines [id:da6780197443194285]
\draw    (178.99,167.4) -- (393.4,167.4) ;
%Straight Lines [id:da9790479690343763]
\draw    (179.39,167) -- (151.25,213.56) ;
%Straight Lines [id:da9225563682209392]
\draw    (393.8,167) -- (420.92,213.12) ;
%Straight Lines [id:da09563387136808865]
\draw    (286.6,167) -- (286.08,213.34) ;
%Straight Lines [id:da3116522709021452]
\draw    (273.92,166.96) -- (270.68,213.56) ;
%Straight Lines [id:da7104288201908657]
\draw    (259.41,166.96) -- (253.18,213.3) ;
%Straight Lines [id:da742779405875688]
\draw    (245.3,166.91) -- (237.52,213.3) ;
%Straight Lines [id:da18844905298889292]
\draw    (232.1,167.18) -- (220.33,213.82) ;
%Straight Lines [id:da35804353174173054]
\draw    (217.96,167.2) -- (201.3,213.56) ;
%Straight Lines [id:da7688901048445682]
\draw    (205.7,167.18) -- (185.02,213.82) ;
%Straight Lines [id:da3470294213255083]
\draw    (192.98,167.2) -- (169.98,213.82) ;
%Straight Lines [id:da35862455135349536]
\draw    (298.62,166.91) -- (302.61,213.56) ;
%Straight Lines [id:da29999796293225955]
\draw    (313.18,167.08) -- (321.21,213.92) ;
%Straight Lines [id:da6206528590435849]
\draw    (327.48,166.91) -- (339.76,213.3) ;
%Straight Lines [id:da9408253594123648]
\draw    (340.68,167.18) -- (357.57,213.82) ;
%Straight Lines [id:da917785587155304]
\draw    (354.8,167.18) -- (374.76,213.56) ;
%Straight Lines [id:da3801603892210079]
\draw    (366.16,167.08) -- (392.26,213.56) ;
%Straight Lines [id:da580723776969265]
\draw    (380.59,167.18) -- (405.77,213.3) ;
%Straight Lines [id:da5336171972507551]
\draw    (155.55,205.39) -- (416.51,204.6) ;
%Straight Lines [id:da956646312420568]
\draw    (160.77,197.48) -- (411.6,196.96) ;
%Straight Lines [id:da2531401201560137]
\draw    (165.32,190.28) -- (407.36,190.06) ;
%Straight Lines [id:da31575285130833475]
\draw    (169.06,183.52) -- (403.31,183.25) ;
%Straight Lines [id:da6000067635957629]
\draw    (172.65,177.85) -- (399.54,177.33) ;
%Straight Lines [id:da36539132370134153]
\draw    (175.41,172.58) -- (396.16,171.79) ;
%Shape: Ellipse [id:dp12271593300544881]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (172.44,205.39) .. controls (172.44,204.59) and (173.19,203.94) .. (174.12,203.94) .. controls (175.06,203.94) and (175.81,204.59) .. (175.81,205.39) .. controls (175.81,206.19) and (175.06,206.84) .. (174.12,206.84) .. controls (173.19,206.84) and (172.44,206.19) .. (172.44,205.39) -- cycle ;
%Shape: Ellipse [id:dp17187409527803665]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (176.2,197.36) .. controls (176.2,196.56) and (176.96,195.91) .. (177.89,195.91) .. controls (178.82,195.91) and (179.58,196.56) .. (179.58,197.36) .. controls (179.58,198.16) and (178.82,198.81) .. (177.89,198.81) .. controls (176.96,198.81) and (176.2,198.16) .. (176.2,197.36) -- cycle ;
%Shape: Ellipse [id:dp3897463489917039]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (179.83,189.94) .. controls (179.83,189.14) and (180.59,188.49) .. (181.52,188.49) .. controls (182.45,188.49) and (183.21,189.14) .. (183.21,189.94) .. controls (183.21,190.74) and (182.45,191.39) .. (181.52,191.39) .. controls (180.59,191.39) and (179.83,190.74) .. (179.83,189.94) -- cycle ;
%Shape: Ellipse [id:dp6651227824721306]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (182.9,183.59) .. controls (182.9,182.79) and (183.66,182.14) .. (184.59,182.14) .. controls (185.52,182.14) and (186.28,182.79) .. (186.28,183.59) .. controls (186.28,184.39) and (185.52,185.04) .. (184.59,185.04) .. controls (183.66,185.04) and (182.9,184.39) .. (182.9,183.59) -- cycle ;
%Shape: Ellipse [id:dp16931876417539748]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (186.11,177.24) .. controls (186.11,176.44) and (186.87,175.79) .. (187.8,175.79) .. controls (188.73,175.79) and (189.49,176.44) .. (189.49,177.24) .. controls (189.49,178.04) and (188.73,178.69) .. (187.8,178.69) .. controls (186.87,178.69) and (186.11,178.04) .. (186.11,177.24) -- cycle ;
%Shape: Ellipse [id:dp011630715757735333]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (189.04,171.85) .. controls (189.04,171.05) and (189.8,170.4) .. (190.73,170.4) .. controls (191.66,170.4) and (192.42,171.05) .. (192.42,171.85) .. controls (192.42,172.65) and (191.66,173.3) .. (190.73,173.3) .. controls (189.8,173.3) and (189.04,172.65) .. (189.04,171.85) -- cycle ;
%Shape: Ellipse [id:dp6352732828874232]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (186.95,205.15) .. controls (186.95,204.35) and (187.71,203.7) .. (188.64,203.7) .. controls (189.57,203.7) and (190.33,204.35) .. (190.33,205.15) .. controls (190.33,205.95) and (189.57,206.6) .. (188.64,206.6) .. controls (187.71,206.6) and (186.95,205.95) .. (186.95,205.15) -- cycle ;
%Shape: Ellipse [id:dp5586918813010036]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (190.44,197.48) .. controls (190.44,196.68) and (191.19,196.03) .. (192.13,196.03) .. controls (193.06,196.03) and (193.82,196.68) .. (193.82,197.48) .. controls (193.82,198.28) and (193.06,198.93) .. (192.13,198.93) .. controls (191.19,198.93) and (190.44,198.28) .. (190.44,197.48) -- cycle ;
%Shape: Ellipse [id:dp9378136236695127]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (193.67,190.5) .. controls (193.67,189.7) and (194.43,189.05) .. (195.36,189.05) .. controls (196.29,189.05) and (197.05,189.7) .. (197.05,190.5) .. controls (197.05,191.3) and (196.29,191.95) .. (195.36,191.95) .. controls (194.43,191.95) and (193.67,191.3) .. (193.67,190.5) -- cycle ;
%Shape: Ellipse [id:dp7452150293769777]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (196.58,183.47) .. controls (196.58,182.67) and (197.33,182.02) .. (198.27,182.02) .. controls (199.2,182.02) and (199.96,182.67) .. (199.96,183.47) .. controls (199.96,184.27) and (199.2,184.92) .. (198.27,184.92) .. controls (197.33,184.92) and (196.58,184.27) .. (196.58,183.47) -- cycle ;
%Shape: Ellipse [id:dp2595074236120878]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (199.51,177.48) .. controls (199.51,176.68) and (200.27,176.03) .. (201.2,176.03) .. controls (202.13,176.03) and (202.89,176.68) .. (202.89,177.48) .. controls (202.89,178.28) and (202.13,178.93) .. (201.2,178.93) .. controls (200.27,178.93) and (199.51,178.28) .. (199.51,177.48) -- cycle ;
%Shape: Ellipse [id:dp8182709430461124]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (201.6,171.85) .. controls (201.6,171.05) and (202.36,170.4) .. (203.29,170.4) .. controls (204.22,170.4) and (204.98,171.05) .. (204.98,171.85) .. controls (204.98,172.65) and (204.22,173.3) .. (203.29,173.3) .. controls (202.36,173.3) and (201.6,172.65) .. (201.6,171.85) -- cycle ;
%Shape: Ellipse [id:dp8721800205864367]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (202.72,205.27) .. controls (202.72,204.47) and (203.47,203.82) .. (204.41,203.82) .. controls (205.34,203.82) and (206.1,204.47) .. (206.1,205.27) .. controls (206.1,206.07) and (205.34,206.72) .. (204.41,206.72) .. controls (203.47,206.72) and (202.72,206.07) .. (202.72,205.27) -- cycle ;
%Shape: Ellipse [id:dp7821722952675314]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (205.51,197.36) .. controls (205.51,196.56) and (206.27,195.91) .. (207.2,195.91) .. controls (208.13,195.91) and (208.89,196.56) .. (208.89,197.36) .. controls (208.89,198.16) and (208.13,198.81) .. (207.2,198.81) .. controls (206.27,198.81) and (205.51,198.16) .. (205.51,197.36) -- cycle ;
%Shape: Ellipse [id:dp6361699950198552]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (207.95,190.5) .. controls (207.95,189.7) and (208.7,189.05) .. (209.64,189.05) .. controls (210.57,189.05) and (211.32,189.7) .. (211.32,190.5) .. controls (211.32,191.3) and (210.57,191.95) .. (209.64,191.95) .. controls (208.7,191.95) and (207.95,191.3) .. (207.95,190.5) -- cycle ;
%Shape: Ellipse [id:dp07429235889252994]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (210.53,183.35) .. controls (210.53,182.55) and (211.29,181.9) .. (212.22,181.9) .. controls (213.15,181.9) and (213.91,182.55) .. (213.91,183.35) .. controls (213.91,184.15) and (213.15,184.8) .. (212.22,184.8) .. controls (211.29,184.8) and (210.53,184.15) .. (210.53,183.35) -- cycle ;
%Shape: Ellipse [id:dp46939239369131425]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (212.63,177.12) .. controls (212.63,176.32) and (213.38,175.67) .. (214.32,175.67) .. controls (215.25,175.67) and (216,176.32) .. (216,177.12) .. controls (216,177.92) and (215.25,178.57) .. (214.32,178.57) .. controls (213.38,178.57) and (212.63,177.92) .. (212.63,177.12) -- cycle ;
%Shape: Ellipse [id:dp47839368197126064]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (214.58,171.73) .. controls (214.58,170.93) and (215.34,170.28) .. (216.27,170.28) .. controls (217.2,170.28) and (217.96,170.93) .. (217.96,171.73) .. controls (217.96,172.53) and (217.2,173.18) .. (216.27,173.18) .. controls (215.34,173.18) and (214.58,172.53) .. (214.58,171.73) -- cycle ;
%Shape: Ellipse [id:dp6735819197452304]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (220.72,205.39) .. controls (220.72,204.59) and (221.48,203.94) .. (222.41,203.94) .. controls (223.34,203.94) and (224.1,204.59) .. (224.1,205.39) .. controls (224.1,206.19) and (223.34,206.84) .. (222.41,206.84) .. controls (221.48,206.84) and (220.72,206.19) .. (220.72,205.39) -- cycle ;
%Shape: Ellipse [id:dp40045376893902485]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (222.81,197.48) .. controls (222.81,196.68) and (223.57,196.03) .. (224.5,196.03) .. controls (225.44,196.03) and (226.19,196.68) .. (226.19,197.48) .. controls (226.19,198.28) and (225.44,198.93) .. (224.5,198.93) .. controls (223.57,198.93) and (222.81,198.28) .. (222.81,197.48) -- cycle ;
%Shape: Ellipse [id:dp002588008650496576]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (224.53,190.5) .. controls (224.53,189.7) and (225.28,189.05) .. (226.21,189.05) .. controls (227.15,189.05) and (227.9,189.7) .. (227.9,190.5) .. controls (227.9,191.3) and (227.15,191.95) .. (226.21,191.95) .. controls (225.28,191.95) and (224.53,191.3) .. (224.53,190.5) -- cycle ;
%Shape: Ellipse [id:dp7269110513068167]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (226.16,183.59) .. controls (226.16,182.79) and (226.92,182.14) .. (227.85,182.14) .. controls (228.78,182.14) and (229.54,182.79) .. (229.54,183.59) .. controls (229.54,184.39) and (228.78,185.04) .. (227.85,185.04) .. controls (226.92,185.04) and (226.16,184.39) .. (226.16,183.59) -- cycle ;
%Shape: Ellipse [id:dp6228752312232548]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (227.7,177.36) .. controls (227.7,176.56) and (228.45,175.91) .. (229.39,175.91) .. controls (230.32,175.91) and (231.08,176.56) .. (231.08,177.36) .. controls (231.08,178.16) and (230.32,178.81) .. (229.39,178.81) .. controls (228.45,178.81) and (227.7,178.16) .. (227.7,177.36) -- cycle ;
%Shape: Ellipse [id:dp5712591071424813]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (229.09,171.97) .. controls (229.09,171.17) and (229.85,170.52) .. (230.78,170.52) .. controls (231.72,170.52) and (232.47,171.17) .. (232.47,171.97) .. controls (232.47,172.77) and (231.72,173.42) .. (230.78,173.42) .. controls (229.85,173.42) and (229.09,172.77) .. (229.09,171.97) -- cycle ;
%Shape: Ellipse [id:dp37415663269795374]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (242.77,171.85) .. controls (242.77,171.05) and (243.53,170.4) .. (244.46,170.4) .. controls (245.39,170.4) and (246.15,171.05) .. (246.15,171.85) .. controls (246.15,172.65) and (245.39,173.3) .. (244.46,173.3) .. controls (243.53,173.3) and (242.77,172.65) .. (242.77,171.85) -- cycle ;
%Shape: Ellipse [id:dp5844680482576305]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (241.79,177.48) .. controls (241.79,176.68) and (242.55,176.03) .. (243.48,176.03) .. controls (244.41,176.03) and (245.17,176.68) .. (245.17,177.48) .. controls (245.17,178.28) and (244.41,178.93) .. (243.48,178.93) .. controls (242.55,178.93) and (241.79,178.28) .. (241.79,177.48) -- cycle ;
%Shape: Ellipse [id:dp27800840767464763]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (240.68,183.23) .. controls (240.68,182.43) and (241.43,181.78) .. (242.37,181.78) .. controls (243.3,181.78) and (244.05,182.43) .. (244.05,183.23) .. controls (244.05,184.03) and (243.3,184.68) .. (242.37,184.68) .. controls (241.43,184.68) and (240.68,184.03) .. (240.68,183.23) -- cycle ;
%Shape: Ellipse [id:dp6309981882755835]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (239.72,190.1) .. controls (239.72,189.3) and (240.48,188.65) .. (241.41,188.65) .. controls (242.34,188.65) and (243.1,189.3) .. (243.1,190.1) .. controls (243.1,190.9) and (242.34,191.55) .. (241.41,191.55) .. controls (240.48,191.55) and (239.72,190.9) .. (239.72,190.1) -- cycle ;
%Shape: Ellipse [id:dp6064458479575909]

>>>>

%Straight Lines [id:da5726274877822322]
\draw [color={rgb, 255:red, 127; green, 117; blue, 117 }  ,draw opacity=1 ] [dash pattern={on 4.5pt off 4.5pt}]  (309.51,73.75) -- (309.87,203.38) ;
\draw [shift={(309.5,70.75)}, rotate = 89.84] [fill={rgb, 255:red, 127; green, 117; blue, 117 }  ,fill opacity=1 ][line width=0.08]  [draw opacity=0] (5.36,-2.57) -- (0,0) -- (5.36,2.57) -- cycle    ;
%Straight Lines [id:da33511458189374754]
\draw    (171.25,233.56) -- (440.92,233.12) ;
%Straight Lines [id:da3398276064046053]
\draw    (198.99,187.4) -- (413.4,187.4) ;
%Straight Lines [id:da7839634174109911]
\draw    (199.39,187) -- (171.25,233.56) ;
%Straight Lines [id:da05894655796955206]
\draw    (413.8,187) -- (440.92,233.12) ;
%Straight Lines [id:da13536583120363344]
\draw    (306.6,187) -- (306.08,233.34) ;
%Straight Lines [id:da4997587586993617]
\draw    (293.92,186.96) -- (290.68,233.56) ;
%Straight Lines [id:da9722317036710604]
\draw    (279.41,186.96) -- (273.18,233.3) ;
%Straight Lines [id:da026737631204194257]
\draw    (265.3,186.91) -- (257.52,233.3) ;
%Straight Lines [id:da1602511216081195]
\draw    (252.1,187.18) -- (240.33,233.82) ;
%Straight Lines [id:da1955990930085778]
\draw    (237.96,187.2) -- (221.3,233.56) ;
%Straight Lines [id:da21157278737030283]
\draw    (225.7,187.18) -- (205.02,233.82) ;
%Straight Lines [id:da7497787157955642]
\draw    (212.98,187.2) -- (189.98,233.82) ;
%Straight Lines [id:da8978850152403992]
\draw    (318.62,186.91) -- (322.61,233.56) ;
%Straight Lines [id:da8571932918195948]
\draw    (333.18,187.08) -- (341.21,233.92) ;
%Straight Lines [id:da28540902944632984]
\draw    (347.48,186.91) -- (359.76,233.3) ;
%Straight Lines [id:da9908810182455174]
\draw    (360.68,187.18) -- (377.57,233.82) ;
%Straight Lines [id:da9097146225861146]
\draw    (374.8,187.18) -- (394.76,233.56) ;
%Straight Lines [id:da7912008612279866]
\draw    (386.16,187.08) -- (412.26,233.56) ;
%Straight Lines [id:da5553223696891176]
\draw    (400.59,187.18) -- (425.77,233.3) ;
%Straight Lines [id:da4854495790277076]
\draw    (175.55,225.39) -- (436.51,224.6) ;
%Straight Lines [id:da8466426333509127]
\draw    (180.77,217.48) -- (431.6,216.96) ;
%Straight Lines [id:da11285301674845338]
\draw    (185.32,210.28) -- (427.36,210.06) ;
%Straight Lines [id:da6415671559000329]
\draw    (189.06,203.52) -- (423.31,203.25) ;
%Straight Lines [id:da09765847114278392]
\draw    (192.65,197.85) -- (419.54,197.33) ;
%Straight Lines [id:da9654913395744491]
\draw    (195.41,192.58) -- (416.16,191.79) ;
%Shape: Ellipse [id:dp5486828293018222]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (192.44,225.39) .. controls (192.44,224.59) and (193.19,223.94) .. (194.12,223.94) .. controls (195.06,223.94) and (195.81,224.59) .. (195.81,225.39) .. controls (195.81,226.19) and (195.06,226.84) .. (194.12,226.84) .. controls (193.19,226.84) and (192.44,226.19) .. (192.44,225.39) -- cycle ;
%Shape: Ellipse [id:dp36608685875382685]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (196.2,217.36) .. controls (196.2,216.56) and (196.96,215.91) .. (197.89,215.91) .. controls (198.82,215.91) and (199.58,216.56) .. (199.58,217.36) .. controls (199.58,218.16) and (198.82,218.81) .. (197.89,218.81) .. controls (196.96,218.81) and (196.2,218.16) .. (196.2,217.36) -- cycle ;
%Shape: Ellipse [id:dp5251439025998383]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (199.83,209.94) .. controls (199.83,209.14) and (200.59,208.49) .. (201.52,208.49) .. controls (202.45,208.49) and (203.21,209.14) .. (203.21,209.94) .. controls (203.21,210.74) and (202.45,211.39) .. (201.52,211.39) .. controls (200.59,211.39) and (199.83,210.74) .. (199.83,209.94) -- cycle ;
%Shape: Ellipse [id:dp4067558888223195]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (202.9,203.59) .. controls (202.9,202.79) and (203.66,202.14) .. (204.59,202.14) .. controls (205.52,202.14) and (206.28,202.79) .. (206.28,203.59) .. controls (206.28,204.39) and (205.52,205.04) .. (204.59,205.04) .. controls (203.66,205.04) and (202.9,204.39) .. (202.9,203.59) -- cycle ;
%Shape: Ellipse [id:dp3570254692613275]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (206.11,197.24) .. controls (206.11,196.44) and (206.87,195.79) .. (207.8,195.79) .. controls (208.73,195.79) and (209.49,196.44) .. (209.49,197.24) .. controls (209.49,198.04) and (208.73,198.69) .. (207.8,198.69) .. controls (206.87,198.69) and (206.11,198.04) .. (206.11,197.24) -- cycle ;
%Shape: Ellipse [id:dp30798846372533184]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (209.04,191.85) .. controls (209.04,191.05) and (209.8,190.4) .. (210.73,190.4) .. controls (211.66,190.4) and (212.42,191.05) .. (212.42,191.85) .. controls (212.42,192.65) and (211.66,193.3) .. (210.73,193.3) .. controls (209.8,193.3) and (209.04,192.65) .. (209.04,191.85) -- cycle ;
%Shape: Ellipse [id:dp1418023342038397]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (206.95,225.15) .. controls (206.95,224.35) and (207.71,223.7) .. (208.64,223.7) .. controls (209.57,223.7) and (210.33,224.35) .. (210.33,225.15) .. controls (210.33,225.95) and (209.57,226.6) .. (208.64,226.6) .. controls (207.71,226.6) and (206.95,225.95) .. (206.95,225.15) -- cycle ;
%Shape: Ellipse [id:dp32047691597756267]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (210.44,217.48) .. controls (210.44,216.68) and (211.19,216.03) .. (212.13,216.03) .. controls (213.06,216.03) and (213.82,216.68) .. (213.82,217.48) .. controls (213.82,218.28) and (213.06,218.93) .. (212.13,218.93) .. controls (211.19,218.93) and (210.44,218.28) .. (210.44,217.48) -- cycle ;
%Shape: Ellipse [id:dp49839354018590987]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (213.67,210.5) .. controls (213.67,209.7) and (214.43,209.05) .. (215.36,209.05) .. controls (216.29,209.05) and (217.05,209.7) .. (217.05,210.5) .. controls (217.05,211.3) and (216.29,211.95) .. (215.36,211.95) .. controls (214.43,211.95) and (213.67,211.3) .. (213.67,210.5) -- cycle ;
%Shape: Ellipse [id:dp8228751417402214]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (216.58,203.47) .. controls (216.58,202.67) and (217.33,202.02) .. (218.27,202.02) .. controls (219.2,202.02) and (219.96,202.67) .. (219.96,203.47) .. controls (219.96,204.27) and (219.2,204.92) .. (218.27,204.92) .. controls (217.33,204.92) and (216.58,204.27) .. (216.58,203.47) -- cycle ;
%Shape: Ellipse [id:dp06953462817928524]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (219.51,197.48) .. controls (219.51,196.68) and (220.27,196.03) .. (221.2,196.03) .. controls (222.13,196.03) and (222.89,196.68) .. (222.89,197.48) .. controls (222.89,198.28) and (222.13,198.93) .. (221.2,198.93) .. controls (220.27,198.93) and (219.51,198.28) .. (219.51,197.48) -- cycle ;
%Shape: Ellipse [id:dp3903462442234402]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (221.6,191.85) .. controls (221.6,191.05) and (222.36,190.4) .. (223.29,190.4) .. controls (224.22,190.4) and (224.98,191.05) .. (224.98,191.85) .. controls (224.98,192.65) and (224.22,193.3) .. (223.29,193.3) .. controls (222.36,193.3) and (221.6,192.65) .. (221.6,191.85) -- cycle ;
%Shape: Ellipse [id:dp4379467974609894]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (222.72,225.27) .. controls (222.72,224.47) and (223.47,223.82) .. (224.41,223.82) .. controls (225.34,223.82) and (226.1,224.47) .. (226.1,225.27) .. controls (226.1,226.07) and (225.34,226.72) .. (224.41,226.72) .. controls (223.47,226.72) and (222.72,226.07) .. (222.72,225.27) -- cycle ;
%Shape: Ellipse [id:dp26193777518096795]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (225.51,217.36) .. controls (225.51,216.56) and (226.27,215.91) .. (227.2,215.91) .. controls (228.13,215.91) and (228.89,216.56) .. (228.89,217.36) .. controls (228.89,218.16) and (228.13,218.81) .. (227.2,218.81) .. controls (226.27,218.81) and (225.51,218.16) .. (225.51,217.36) -- cycle ;
%Shape: Ellipse [id:dp019861246471317262]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (227.95,210.5) .. controls (227.95,209.7) and (228.7,209.05) .. (229.64,209.05) .. controls (230.57,209.05) and (231.32,209.7) .. (231.32,210.5) .. controls (231.32,211.3) and (230.57,211.95) .. (229.64,211.95) .. controls (228.7,211.95) and (227.95,211.3) .. (227.95,210.5) -- cycle ;
%Shape: Ellipse [id:dp1381162876501707]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (230.53,203.35) .. controls (230.53,202.55) and (231.29,201.9) .. (232.22,201.9) .. controls (233.15,201.9) and (233.91,202.55) .. (233.91,203.35) .. controls (233.91,204.15) and (233.15,204.8) .. (232.22,204.8) .. controls (231.29,204.8) and (230.53,204.15) .. (230.53,203.35) -- cycle ;
%Shape: Ellipse [id:dp5428095668243373]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (232.63,197.12) .. controls (232.63,196.32) and (233.38,195.67) .. (234.32,195.67) .. controls (235.25,195.67) and (236,196.32) .. (236,197.12) .. controls (236,197.92) and (235.25,198.57) .. (234.32,198.57) .. controls (233.38,198.57) and (232.63,197.92) .. (232.63,197.12) -- cycle ;
%Shape: Ellipse [id:dp18211764432101352]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (234.58,191.73) .. controls (234.58,190.93) and (235.34,190.28) .. (236.27,190.28) .. controls (237.2,190.28) and (237.96,190.93) .. (237.96,191.73) .. controls (237.96,192.53) and (237.2,193.18) .. (236.27,193.18) .. controls (235.34,193.18) and (234.58,192.53) .. (234.58,191.73) -- cycle ;
%Shape: Ellipse [id:dp75878279205988]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (240.72,225.39) .. controls (240.72,224.59) and (241.48,223.94) .. (242.41,223.94) .. controls (243.34,223.94) and (244.1,224.59) .. (244.1,225.39) .. controls (244.1,226.19) and (243.34,226.84) .. (242.41,226.84) .. controls (241.48,226.84) and (240.72,226.19) .. (240.72,225.39) -- cycle ;
%Shape: Ellipse [id:dp4571990490264608]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (242.81,217.48) .. controls (242.81,216.68) and (243.57,216.03) .. (244.5,216.03) .. controls (245.44,216.03) and (246.19,216.68) .. (246.19,217.48) .. controls (246.19,218.28) and (245.44,218.93) .. (244.5,218.93) .. controls (243.57,218.93) and (242.81,218.28) .. (242.81,217.48) -- cycle ;
%Shape: Ellipse [id:dp4013248465635957]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (244.53,210.5) .. controls (244.53,209.7) and (245.28,209.05) .. (246.21,209.05) .. controls (247.15,209.05) and (247.9,209.7) .. (247.9,210.5) .. controls (247.9,211.3) and (247.15,211.95) .. (246.21,211.95) .. controls (245.28,211.95) and (244.53,211.3) .. (244.53,210.5) -- cycle ;
%Shape: Ellipse [id:dp7663905432089348]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (246.16,203.59) .. controls (246.16,202.79) and (246.92,202.14) .. (247.85,202.14) .. controls (248.78,202.14) and (249.54,202.79) .. (249.54,203.59) .. controls (249.54,204.39) and (248.78,205.04) .. (247.85,205.04) .. controls (246.92,205.04) and (246.16,204.39) .. (246.16,203.59) -- cycle ;
%Shape: Ellipse [id:dp37843272203409817]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (247.7,197.36) .. controls (247.7,196.56) and (248.45,195.91) .. (249.39,195.91) .. controls (250.32,195.91) and (251.08,196.56) .. (251.08,197.36) .. controls (251.08,198.16) and (250.32,198.81) .. (249.39,198.81) .. controls (248.45,198.81) and (247.7,198.16) .. (247.7,197.36) -- cycle ;
%Shape: Ellipse [id:dp6447080382369588]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (249.09,191.97) .. controls (249.09,191.17) and (249.85,190.52) .. (250.78,190.52) .. controls (251.72,190.52) and (252.47,191.17) .. (252.47,191.97) .. controls (252.47,192.77) and (251.72,193.42) .. (250.78,193.42) .. controls (249.85,193.42) and (249.09,192.77) .. (249.09,191.97) -- cycle ;
%Shape: Ellipse [id:dp1815955543825718]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (262.77,191.85) .. controls (262.77,191.05) and (263.53,190.4) .. (264.46,190.4) .. controls (265.39,190.4) and (266.15,191.05) .. (266.15,191.85) .. controls (266.15,192.65) and (265.39,193.3) .. (264.46,193.3) .. controls (263.53,193.3) and (262.77,192.65) .. (262.77,191.85) -- cycle ;
%Shape: Ellipse [id:dp8880224712841644]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (261.79,197.48) .. controls (261.79,196.68) and (262.55,196.03) .. (263.48,196.03) .. controls (264.41,196.03) and (265.17,196.68) .. (265.17,197.48) .. controls (265.17,198.28) and (264.41,198.93) .. (263.48,198.93) .. controls (262.55,198.93) and (261.79,198.28) .. (261.79,197.48) -- cycle ;
%Shape: Ellipse [id:dp4989200469883939]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (260.68,203.23) .. controls (260.68,202.43) and (261.43,201.78) .. (262.37,201.78) .. controls (263.3,201.78) and (264.05,202.43) .. (264.05,203.23) .. controls (264.05,204.03) and (263.3,204.68) .. (262.37,204.68) .. controls (261.43,204.68) and (260.68,204.03) .. (260.68,203.23) -- cycle ;
%Shape: Ellipse [id:dp28395245427438764]
\draw  [fill={rgb, 255:red, 118; green, 113; blue, 113 }  ,fill opacity=1 ] (259.72,210.1) .. controls (259.72,209.3) and (260.48,208.65) .. (261.41,208.65) .. controls (262.34,208.65) and (263.1,209.3) .. (263.1,210.1) .. controls (263.1,210.9) and (262.34,211.55) .. (261.41,211.55) .. controls (260.48,211.55) and (259.72,210.9) .. (259.72,210.1) -- cycle ;
%Shape: Ellipse [id:dp03156593400590513]
